---
title: "Pilot Data Cleaner"
author: "Daniel K Baissa, Melani Cammett, and Aytug Sasmaz"
date: "December 12, 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(rstanarm)
library(tidyverse)
library(data.table)
library(MASS)
```

## Loading in data

I will start by creating a function to automatically set up the data.

All of this is a work in progress
```{r loading datasets}
# Creating a function to load datasets

data_cleaner <- function(d){
 
  df <- read_csv(d) %>% #reading in the data
  slice(c(-1, -2)) #qualtrics adds 2 rows of unnecessary headers. This removes them.

# Cleaning up the conjoint data. 
# Note, this is not very efficient memory wise 
# and may need to be tuned up for larger datasets

names <- colnames(df)

new_names <- paste0(1:243, "_conjoint_friend1")
new_names2 <- paste0(1:243, "_conjoint_friend2")

df2 <- df %>% 
  setnames(old = names[246:488], new = new_names) %>%
  setnames(old = names[489:731], new = new_names2)
    
  
test2 <- df2 %>%  
    pivot_longer(
          cols = ends_with("friend1"),
          names_to = "Conjoint_first_permutation",
          values_to = "Conjoint_first_permutation_answer") %>%
  filter(!is.na(Conjoint_first_permutation_answer)) %>%  
    pivot_longer(
          cols = ends_with("_friend2"),
          names_to = "Conjoint_second_permutation",
          values_to = "Conjoint_second_permutation_answer") %>%
    filter(!is.na(Conjoint_second_permutation_answer)) %>%
   pivot_longer(
          cols = starts_with("ptt"),
          names_to = "Petition_Experiment_Treatment",
          values_to = "Petition_Experiment_Treatment_Answer") %>%
  filter(!is.na(Petition_Experiment_Treatment_Answer))
}




```


Now that the function is created, we can use it to make our data.
There will be a warning, but it is totally ok for now.

```{r loading data, message=FALSE, warning=FALSE}

csv <- c("D:/Lebanon_data/LEB Youth Civic Engagement ENG - postcut_December 11, 2020_21.29.csv",
         "D:/Lebanon_data/LEB Youth Civic Engagement ARA - postcut_December 11, 2020_22.09.csv")

ENG <- data_cleaner(csv[1])
ARA <- data_cleaner(csv[2])

# For now I will remove the Q_RecaptchaScore

ARA$Q_RecaptchaScore <- NULL
ENG$Q_RecaptchaScore <- NULL

# There is an extra att_women in English "att_women_4"

ENG$att_women_4 <- NULL


# For now I am just going to force the two datasets to have the same variable names

ARA <- ARA %>% 
  setnames(old = colnames(ARA), new = colnames(ENG)) 

df <- rbind(ENG, ARA)

```

## Demographic distribution 

```{r gender, echo=FALSE}

# Female = 10
# Male = 9

df$gender <- 2
df$gender[which(as.double(df$dem_gender) == 10)] <- 1
df$gender[which(as.double(df$dem_gender) == 9)] <- 0

summary(df$gender) #Median person is a man and there seems to be a lot more men






```

```{r}

ggplot(df, aes(x = gender))+
  geom_histogram(bins = 3, fill="white", color="black")+
  labs(title="Gender Distribution",x="", y = "Count")+
  theme_classic()

```

### Religious demographics

```{r}
summary(as.double(df$att_identity))
ggplot(df, aes(x = as.double(att_identity)))+
  geom_histogram(bins = 7, fill="white", color="black")+
  labs(title="att_identity",x="", y = "Count")+
  theme_classic()

```

```{r}

```


### Income distribution

Below are some statements related to your household income. Which of these statements comes closest to describing your household income?
```{r}
summary(as.double(df$dem_income1))

#line of code

```
```{r}
ggplot(df, aes(x = as.double(dem_income1)))+
  geom_histogram(bins = 4, fill="white", color="black")+
  labs(title="Which of these statements comes closest to describing your household income?",x="", y = "Count")+
  theme_classic()

```
To the best of your knowledge, what is your household’s total net income in Lebanese Liras (L.L.) in a typical month? 

```{r}
summary(as.double(df$dem_income2))


```
```{r}
ggplot(df, aes(x = as.double(dem_income2)))+
  geom_histogram(bins = 9, fill="white", color="black")+
  labs(title="what is your household’s total net income in Lebanese Liras (L.L.) in a typical month?",x="", y = "Count")+
  theme_classic()

```


What is the highest level of education that you completed?

```{r}
summary(as.double(df$dem_edu))

```
```{r}
ggplot(df, aes(x = as.double(dem_edu)))+
  geom_histogram(bins = 10, fill="white", color="black")+
  labs(title="What is the highest level of education that you completed?",x="", y = "Count")+
  theme_classic()

```

What is your father’s education level? 

```{r}
summary(as.double(df$dem_fatheredu))
ggplot(df, aes(x = as.double(dem_fatheredu)))+
  geom_histogram(bins = 11, fill="white", color="black")+
  labs(title="What is your father’s education level? ",x="", y = "Count")+
  theme_classic()

```


```{r}

summary(as.double(df$dem_motheredu))
ggplot(df, aes(x = as.double(dem_motheredu)))+
  geom_histogram(bins = 10, fill="white", color="black")+
  labs(title="What is your mother’s education level?",x="", y = "Count")+
  theme_classic()

```

Mother's are better educated than fathers in this sample

## Petition Signing distribution 

How many people actually signed the petition?
Lets find out. 

```{r Signing, echo=FALSE}

ggplot(df, aes(x = as.double(Q144)))+
  geom_histogram(bins = 3, fill="white", color="black")+
  labs(title="Petition Signing",x="", y = "Count")+
  theme_classic()

```

Lets do some basic stats on the petition experiment. 
Here is a simple logistic regression to see if the control group is different from any of the treatments. 

```{r too simple logits}

# colnames(df)
# unique(df$Petition_Experiment_Treatment)

df2 <- df %>% 
  filter(Petition_Experiment_Treatment == "ptt_treat_control_fo" | Petition_Experiment_Treatment == "ptt_treat_eco_foll") 

df2$pt_econ_treatment <- 0
df2$pt_econ_treatment[which(df2$Petition_Experiment_Treatment == "ptt_treat_eco_foll")] <- 1
df2$signed <- 0
df2$signed[which(df2$Q144 > 0)] <- 1

test <- glm(signed ~ pt_econ_treatment, data = df2, family = binomial())

summary(test)



```


```{r warning=TRUE, include=FALSE}
m <- polr(as.factor(Q144) ~ Petition_Experiment_Treatment , data = df, Hess=TRUE)
# summary(m)
## store table
(ctable <- coef(summary(m)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

```

```{r}
## combined table
(ctable <- cbind(ctable, "p value" = p))
```


The Covid Treatment was the treatment left out for comparison by the model. Lets take a look at that.

```{r, Ordered Logit detail, include=FALSE}
df2 <- df %>%
  filter(Petition_Experiment_Treatment == "ptt_treat_control_fo" | Petition_Experiment_Treatment == "ptt_cont_foll")



m2 <- polr(as.factor(Q144) ~ Petition_Experiment_Treatment , data = df2, Hess=TRUE)
# summary(m2)
## store table
(ctable <- coef(summary(m2)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

```

```{r}
signif((ctable <- cbind(ctable, "p value" = p)),3)
```

Something appears to be going on here, but the N is so small that it could still be chance
