---
title: "Pilot Data Cleaner"
author: "Daniel K Baissa, Melani Cammett, and Aytug Sasmaz"
date: "December 12, 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(rstanarm)
library(tidyverse)
library(data.table)
library(dplyr)

```

## Loading in data

I will start by creating a function to automatically set up the data.

All of this is a work in progress

```{r loading datasets, include=FALSE}


# Creating a function to load datasets

data_cleaner <- function(d){
 
  df <- read_csv(d) %>% #reading in the data
  slice(c(-1, -2)) #qualtrics adds 2 rows of unnecessary headers. This removes them.

# Cleaning up the conjoint data. 
# Note, this is not very efficient memory wise 
# and may need to be tuned up for larger datasets

names <- colnames(df)

conjoint1 <- df %>% 
  select(ends_with("_Q171") | ends_with("_friend1")) %>% 
  colnames()

conjoint2 <- df %>% 
  select(ends_with("_Q172")| ends_with("_friend2")) %>% 
  colnames()

new_names <- paste0(1:243, "_conjoint_friend1")
new_names2 <- paste0(1:243, "_conjoint_friend2")

df2 <- df %>% 
  setnames(old = conjoint1[1:243], new = new_names) %>%
  setnames(old = conjoint2[1:243], new = new_names2)
  
  
test2 <- df2 %>%  
    pivot_longer(
          cols = ends_with("friend1"),
          names_to = "Conjoint_first_permutation",
          values_to = "Conjoint_first_permutation_answer") %>%
  filter(!is.na(Conjoint_first_permutation_answer)) %>%  
    pivot_longer(
          cols = ends_with("_friend2"),
          names_to = "Conjoint_second_permutation",
          values_to = "Conjoint_second_permutation_answer") %>%
    filter(!is.na(Conjoint_second_permutation_answer)) %>%
   pivot_longer(
          cols = starts_with("ptt"),
          names_to = "Petition_Experiment_Treatment",
          values_to = "Petition_Experiment_Treatment_Answer") %>%
  filter(!is.na(Petition_Experiment_Treatment_Answer))
}




```


Now that the function is created, we can use it to make our data.
There will be a warning, but it is totally ok for now.

```{r loading data, include=FALSE}



csv <- c("D:/Lebanon_data/LEB Youth Civic Engagement ENG - postcut_December 13, 2020_17.38.csv",
         "D:/Lebanon_data/LEB Youth Civic Engagement ARA - postcut_December 13, 2020_17.36.csv")

ENG <- data_cleaner(csv[1])
ARA <- data_cleaner(csv[2])

# For now I will remove the Q_RecaptchaScore

ARA$Q_RecaptchaScore <- NULL
ENG$Q_RecaptchaScore <- NULL

# There is an extra att_women in English "att_women_4"

ENG$att_women_4 <- NULL


# For now I am just going to force the two datasets to have the same variable names

ARA <- ARA %>% 
  setnames(old = colnames(ARA), new = colnames(ENG)) 

df <- rbind(ENG, ARA)

df <- df %>% 
  mutate(Petition_Experiment_Treatment = recode(Petition_Experiment_Treatment,                                                                                                                  "ptt_treat_control_fo" = "ptt_cont_foll"))


```

## How Many Observations

As of the evening of December 13 Qualtrics recorded the following total of responses:  

```{r echo=FALSE, warning=FALSE}

length(read.csv(csv[1])[,1]) + length(read.csv(csv[2])[,1])

```


We can use approximately:

```{r echo=FALSE, warning=FALSE}
length(df$StartDate)
```
Of which, most if not all are ~100% complete.

The large discrepancy is because Qualtrics automatically completes the observation after 72 hours.
\newpage

## Manipulation Check

It looks like respondants are heavily biased towards saying "has resulted in corruption and mismanagement of the economy". It was really high even in the control group
```{r include=FALSE}

df <- df %>% 
  mutate(Manipulation_Check = recode(petition_manip_check,
                             `1` = "ensures that the security situation remains stable",
                             `2` = "has resulted in corruption and mismanagement of the economy",
                             `3` = "ensures that all confessional groups get access to benefits",
                             `4` = "encourages the sectarian parties to provide benefits to the population",
                             `5` = "I do not remember"))

df <- df %>% 
  mutate(Manipulation_Check2 = recode(petition_manip_check,
                             `1` = "security remains stable",
                             `2` = "corruption and mismanagement",
                             `3` = "confessional get benefits",
                             `4` = "sectarian parties benefits",
                             `5` = "I do not remember"))


df <- df %>% 
  mutate(Petition_Experiment_Treatment_Check = recode(Petition_Experiment_Treatment,
                                                  "ptt_treat_sec_foll" = "Security Benefits",
                                                  "ptt_treat_eco_foll" = "Economic Hardship",
                                                  "ptt_treat_bft_foll" = "Economic Benefits",
                                                  "ptt_treat_cor_foll" = "Coronavirus Response",
                                                  "ptt_cont_foll" = "Control"))
                                                                    


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# plot_data <- df %>% 
#   group_by(Manipulation_Check2, Petition_Experiment_Treatment_Check) %>% 
#   tally %>% 
#   mutate(percent = n/sum(n))
# 

df %>% 
  ggplot(mapping = aes(x = Manipulation_Check2)) +
  geom_bar()+
  facet_wrap(~Petition_Experiment_Treatment_Check)+
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x = "")
  
```

\newpage

## Demographic distributions 

By governorate

```{r include=FALSE}

df <- df %>% 
  mutate(Governorate= recode(dem_live_1,
                             `1` = "Akkar",
                             `127` = "Baalbek-Hermel",
                             `213` = "Beirut",
                             `216` = "Beqaa",
                             `307` = "Mount Lebanon",
                             `639` = "Nabatieh",
                             "763" = "North Lebanon",
                             `914` = "South Lebanon"))




```


```{r gender, include=FALSE}



# Female = 10
# Male = 9

df$gender <- "Other"
df$gender[which(as.double(df$dem_gender) == 10)] <- "Female"
df$gender[which(as.double(df$dem_gender) == 9)] <- "Male"

df$gender





```

```{r echo=FALSE, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}



ggplot(df, mapping = aes(x = gender)) +
  geom_bar() +
  labs(title="Gender Distribution",x="", y = "Count")+
  facet_wrap(~Governorate)
  

```

### Age demographics

```{r, echo=FALSE}
ggplot(df, mapping = aes(x = dem_birthyear, fill = gender)) +
  geom_bar() +
  labs(title="Birth Year Distribution",x="", y = "Count")+
  facet_wrap(~Governorate)+
  theme(axis.text.x = element_text(angle = 90))
  
```


### Religious demographics

```{r echo=FALSE, fig.height=8, fig.width=7, message=FALSE, warning=FALSE}

df <- df %>% 
  mutate(Confession= recode(att_confession,
                            `1` = "Maronite",
                            `2` = "Greek Orthodox",
                            `3` = "Greek Catholic",
                            `4` = "Armenian Orthodox",
                            `5` = "Armenian Catholic",
                            `6` = "Protestant",
                            `7` = "Syriac Orthodox",
                            `8` = "Syriac Catholic",
                            `9` = "Nestorian Assyrian",
                            `10` = "Chaldean",
                            `11` = "Coptic",
                            `12` = "Roman Catholic",
                            `13` = "Sunni Muslim",
                            `14` = "Shia Muslim",
                            `15` = "Ismaili",
                            `16` = "Druze",
                            `17` = "Alawite",
                            `18` = "Jewish"))

ggplot(df, mapping = aes(x = Confession, fill = gender)) +
  geom_bar() +
  labs(title="What is your confession as officially listed on your registration card?",x="", y = "Count")+
  facet_wrap(~Governorate)+
  theme(axis.text.x = element_text(angle = 90))

```

```{r, echo=FALSE}

```


### Income distribution

Below are some statements related to your household income. Which of these statements comes closest to describing your household income?
```{r}
summary(as.double(df$dem_income1))


```
```{r echo=FALSE, message=FALSE, warning=FALSE}


ggplot(df, mapping = aes(x = dem_income1, fill = gender)) +
  geom_bar() +
  labs(title="Household Income?",x="", y = "Count")+
  facet_wrap(~Governorate)+
  theme(axis.text.x = element_text(angle = 90))

```

```{r echo=FALSE, message=FALSE, warning=FALSE}


ggplot(df, mapping = aes(x = dem_income1)) +
  geom_bar() +
  labs(title="Household Income?",x="", y = "Count")+
  facet_wrap(~gender)+
  theme(axis.text.x = element_text(angle = 90))

```


To the best of your knowledge, what is your household’s total net income in Lebanese Liras (L.L.) in a typical month? 

```{r}
summary(as.double(df$dem_income2))


```
```{r echo=FALSE, message=FALSE, warning=FALSE}


ggplot(df, mapping = aes(x = dem_income2)) +
  geom_bar() +
  labs(title="What is your household’s total net income in Lebanese Liras a month?",x="", y = "Count")+
  facet_wrap(~gender)+
  theme(axis.text.x = element_text(angle = 90))

```

```{r echo=FALSE, message=FALSE, warning=FALSE}


ggplot(df, mapping = aes(x = dem_income2, fill = gender)) +
  geom_bar() +
  labs(title="What is your household’s total net income in Lebanese Liras a month?",x="", y = "Count")+
  facet_wrap(~Governorate)+
  theme(axis.text.x = element_text(angle = 90))

```

What is the highest level of education that you completed?

```{r}
summary(as.double(df$dem_edu))

```
```{r}
ggplot(df, aes(x = as.double(dem_edu)))+
  geom_histogram(bins = 10, fill="white", color="black")+
  labs(title="What is the highest level of education that you completed?",x="", y = "Count")+
  theme_classic()

```

What is your father’s education level? 

```{r}
summary(as.double(df$dem_fatheredu))
ggplot(df, aes(x = as.double(dem_fatheredu)))+
  geom_histogram(bins = 11, fill="white", color="black")+
  labs(title="What is your father’s education level? ",x="", y = "Count")+
  theme_classic()

```


```{r}

summary(as.double(df$dem_motheredu))
ggplot(df, aes(x = as.double(dem_motheredu)))+
  geom_histogram(bins = 10, fill="white", color="black")+
  labs(title="What is your mother’s education level?",x="", y = "Count")+
  theme_classic()

```

Mother's are better educated than fathers in this sample

## Petition Signing distribution 

How many people actually signed the petition?
Lets find out. 

```{r Signing, echo=FALSE}

ggplot(df, aes(x = as.double(Q144)))+
  geom_histogram(bins = 3, fill="white", color="black")+
  labs(title="Petition Signing",x="", y = "Count")+
  theme_classic()

```

Lets do some basic stats on the petition experiment. 
Here is a simple logistic regression to see if the control group is different from any of the treatments. 

```{r too simple logits}

# colnames(df)
# unique(df$Petition_Experiment_Treatment)

df2 <- df %>% 
  filter(Petition_Experiment_Treatment == "ptt_cont_foll" | Petition_Experiment_Treatment == "ptt_treat_eco_foll") 

df2$pt_econ_treatment <- 0
df2$pt_econ_treatment[which(df2$Petition_Experiment_Treatment == "ptt_treat_eco_foll")] <- 1
df2$signed <- 0
df2$signed[which(df2$Q144 > 0)] <- 1

test <- glm(signed ~ pt_econ_treatment, data = df2, family = binomial())

summary(test)



```


```{r warning=TRUE, include=FALSE}
library(MASS)
m <- polr(as.factor(Q144) ~ Petition_Experiment_Treatment + UserLanguage , data = df, Hess=TRUE)
# summary(m)
## store table
(ctable <- coef(summary(m)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

```

```{r message=FALSE, warning=FALSE}
## combined table
(ctable <- cbind(ctable, "p value" = p))
```


The Covid Treatment was the treatment left out for comparison by the model. Lets take a look at that.

```{r, Ordered Logit detail, include=FALSE}
df2 <- df %>%
  filter(Petition_Experiment_Treatment == "ptt_cont_foll" | Petition_Experiment_Treatment == "ptt_treat_cor_foll")


m2 <- polr(as.factor(Q144) ~ Petition_Experiment_Treatment + UserLanguage , data = df2, Hess=TRUE)
# summary(m2)
## store table
(ctable <- coef(summary(m2)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

```

```{r}
signif((ctable <- cbind(ctable, "p value" = p)),3)
```

Something appears to be going on here, but the N is so small that it could still be chance
